FoRTE baseline

### 2019-03-27 analysis/paper/paper.Rmd
Add another parameter means plot

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)

@@

@@

@@

Different parameter combinations produce

>>>>

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
```

@@

```{r captions_uncertainty}
annual_means_cap <- paste(
  "Total annual gross (GPP) and net (NPP) primary productivity,",
  "and maximum annual leaf area index (LAI)",
  "from ED2 parameter ensemble simulations.",
  "Red lines are mean (solid) and min/max (dashed) values",
  "from Hardiman et al. (2013)."
)

@@

```{r annual_means, fig.cap = annual_means_cap, fig.dim = c(5, 7)}
readd(old_ensemble_plot)
```

`r mdcap(annual_means_cap)`

@@

Different parameter combinations produce qualitatively different successional outcomes.
